Combinatorics of the geometry of Wilson loop diagrams II: Grassmann necklaces, dimensions, and denominators

### 2019-09-13 GWLDCII.tex
removed and added some commments

\begin{lem}\label{lem no fourth vertex}
Let $W$ be an admissible Wilson loop diagram containing at least one propagator. For any $i \in [n]$ and for any $p \in \cP$, $I_i(p)$ is not maximal (with respect to $<_i$) amongst the vertices that support $p$.
\end{lem} 
\sanote{wanted to rewrite this lemma to emphasize the fact that we are using the same properties of Alg 3.7 over and over again, and have these principals set apart in a remark}
\begin{proof}
Suppose for contradiction that we have $i \in [n]$ and $p \in \cP$ such that $I_i(p)$ is $<_i$-maximal in $V(p)$. There are two possibilities, which are illustrated in Figure~\ref{fig:no fourth vertex}: either $p = (i-1,b)$ for some $b$ (so $i$ and $I_i(p) = i-1$ are the two ends of a single edge), or $p = (a,b)$ with $i\leq_i a <_i b$ and $I_i(p) = b+1$.

@@

\note{Following two paragraphs added to replace the sentence ``clearly $n-3 \not\in I_1^V$''}
We first show that $n-3 \not\in I_1^V$. In Case 1, the only way we could have $n-3 \in I_1^V$ is if $V$ admits some propagator $r$ with $I_1(r) = n-3$; from the figure, one end of $r$ would have to lie on edge $n-4$, and by Lemma~\ref{lem no fourth vertex} the other end would have to lie on edge $n-1$ or $n$. However, if $r = (n-4,n-1)$ then by [remark following cyclic intervals lemma] we would have $I_1^V(r) = n-4$, while if $r = (n-4,n)$ then $r$ is the clockwise-most propagator supported on vertex 1 and we would have $I_1^V(r) = 1$. Either way, we have $I_1^V(r) \neq n-3$.

In Case 2 the only propagator supported on vertex $n-3$ in $V$ is $q$, and by [cyclic intervals remark] we have $I_{n-1}^V(q) = n-5$. Further, it must also be the case that $I_n^V(q) = n - 5$: if $n-1$ is non-supporting in $V$ then this is immediate, while if there exists a propagator $r$ in $V$ with $I_{n-1}^V(r) = n-1$ then $r$ lies on edge $n-1$ and is the clockwise-most propagator supported on vertex $n$, so $I_n^V(r) = n$ and the remainder of $I_n^V$ proceeds identically to $I_{n-1}^V$. Thus $I_n^V(q) = n-5$, so by [cyclic intervals lemma or remark] we have $I_1^V(q) \in \{n-5,n-4\}$; in particular, $I_1^V(q)\neq n-3$.

>>>>

\begin{lem}\label{lem no fourth vertex}
Let $W$ be an admissible Wilson loop diagram containing at least one propagator. For any $i \in [n]$ and for any $p \in \cP$, $I_i(p)$ is not maximal (with respect to $<_i$) amongst the vertices that support $p$.
\end{lem} 
\begin{proof}
Suppose for contradiction that we have $i \in [n]$ and $p \in \cP$ such that $I_i(p)$ is $<_i$-maximal in $V(p)$. There are two possibilities, which are illustrated in Figure~\ref{fig:no fourth vertex}: either $p = (i-1,b)$ for some $b$ (so $i$ and $I_i(p) = i-1$ are the two ends of a single edge), or $p = (a,b)$ with $i\leq_i a <_i b$ and $I_i(p) = b+1$.

@@

\note{Following two paragraphs added to replace the sentence ``clearly $n-3 \not\in I_1^V$''}
We first show that $n-3 \not\in I_1^V$. In Case 1, the only way we could have $n-3 \in I_1^V$ is if $V$ admits some propagator $r$ with $I_1(r) = n-3$; from the figure, one end of $r$ would have to lie on edge $n-4$, and by Lemma~\ref{lem no fourth vertex} the other end would have to lie on edge $n-1$ or $n$. However, if $r = (n-4,n-1)$ then by [remark following cyclic intervals lemma] \hlfix{we would have $I_1^V(r) = n-4$}{because if it contributed $n-3$ it would never be able to contribute $n-4$?}, while if $r = (n-4,n)$ then $r$ is the clockwise-most propagator supported on vertex 1 and we would have $I_1^V(r) = 1$. Either way, we have $I_1^V(r) \neq n-3$.

In Case 2 the only propagator supported on vertex $n-3$ in $V$ is $q$, and by [cyclic intervals remark] we \hlfix{have $I_{n-1}^V(q) = n-5$}{Because $I_{n-2}^V(q) = n-2$ and Lemma \ref{lem no vourht vertex} prevents $I_{n-1}^V(q) = n-2$?}. Further, it must also be the case that $I_n^V(q) = n - 5$: if $n-1$ is non-supporting in $V$ then this is immediate, while if there exists a propagator $r$ in $V$ with $I_{n-1}^V(r) = n-1$ then $r$ lies on edge $n-1$ and is the clockwise-most propagator supported on vertex $n$, so $I_n^V(r) = n$ and the remainder of $I_n^V$ proceeds identically to $I_{n-1}^V$. Thus $I_n^V(q) = n-5$, so by [cyclic intervals lemma or remark] we have $I_1^V(q) \in \{n-5,n-4\}$; in particular, $I_1^V(q)\neq n-3$.
